### 2011-07-19 Text/paper.tex
A bit of changes.

\documentclass{article}
\usepackage[numbers,sort&compress]{natbib}
\usepackage{graphicx}
\usepackage{amssymb,amsmath}
\usepackage{bm}
\usepackage{color}
\usepackage{tabularx}
\begin{document}
\section{Motivation}
The mass transfer is a very important characteristic for design of the microchannels. It allows to
properly understand the properties of the channel length, channel length to microchannel ratios. In
what follows the mass transfer associated with the bubble moving in the microchannel through liquid
medium.

A few questions need to be addressed:
\begin{description}
 \item[I] The efficiency of the mass transfer depending on the capillary number. For small capillary
numbers as $Ca<0.6$ for square microchannels there is a vortex in the moving with the bubble
reference frame, which certainly will improve the corresponding mass transfer. Note that the flow
patterns highly depend on the number of parameters as the slug length, the thickness of the
thickness and the existence of the vortex in front of the bubble. There are some available
correlations in literature \cite{bercic-mass,kreutzer-overview} and one of the particular goal of
this study is to study mass transfer dependence on the number of parameters. As well to validate or
to come up with another correlation describing the mass transfer.

@@

The volumetric mass transfer coefficient is calculated according to the work of
\citet{vanbaten-circular}. The concentration flux is calculated as the difference between overall
average concentration taken in the whole domain ($C_{overall}=\int_{V} C \mathrm{d}V /V$) 
{\color{red} (In this particular moment I don't know whether to take the Volume of whole domain or
just the liquid phase. I will go for whole domain.)}
at time
$t_1$ and time $t_2$ divided on the time difference $t_2-t_1$. Then the volumetric mass transfer
coefficient is calculated as:
\begin{equation}
\label{main:simulation:equation}
k_L a=\frac{\text{Flux}}{C_s-C_{outlet}} \frac{\text{bubble surface area}}{\text{unit cell volume}},
\end{equation}
where $C_{outlet}=\int{C U_{outlet}\mathrm{d}A}/\int{U_{outlet}\mathrm{d}A}$. 
{\color{red} Do not understand why we need this ratio bubble surface area/unit cell volume. In this
case the dimensional units do not coincide. In the calculations I will avoid it until further
clearance.}
To properly do
non-dimensioanalization one needs to insure the time conversion factor when the flux is calculated
inside the lattice Botlzmann system. The time conversion can be easily obtained:
\begin{equation}
\begin{aligned}
&U_{LB}=U_{phys}\frac{\Delta t}{\Delta x}\\
&\Delta t=\frac{U_{LB}}{U_{phys}}\Delta x\\
&\Delta t=\frac{1.5\,\mathrm{mm}}{200} \frac{0.0559}{0.902\,\mathrm{m/s}}=4.64\times
10^{-7}\,\mathrm{s} 
\end{aligned}
\end{equation}

@@

The corresponding volumetric mass transfer coefficients depending on the velocity are indicated in
Table \ref{table:lengths}.

\section{Simulation results}
\subsection{Steady-state}
Using Eq.\ref{main:simulation:equation} we calculated the mass transfer coefficient. One can see
the plots for the mass transfer coefficient versus time in Fig. \ref{fig:steady:state}. We state as
a steady-state condition the average of  
\begin{figure}
\includegraphics[width=\textwidth]{Figures/steady_state.eps}
\caption{The mass transfer coefficient vs. time iterations. One can see that the pseudo steady
state can be reached after $500000$. The mass transfer coefficient is taken as the average from
$500000$ to $1000000$.\label{fig:steady:state}}
\end{figure}

>>>>

\documentclass{article}
\usepackage[numbers,sort&compress]{natbib}
\usepackage{graphicx}
\usepackage{amssymb,amsmath}
\usepackage{bm}
\usepackage{color}
\usepackage{tabularx}
\begin{document}
\section{Motivation}
The mass transfer is a very important characteristic for microchannels  design. It allows to
properly design a microchannel properties as the channel length, channel length to ensure best possible chemical reactions . In
what follows the mass transfer associated with the bubble moving in the microchannel through liquid
medium is studied.

A few questions need to be addressed:
\begin{description}
 \item[I] The efficiency of the mass transfer depending on the capillary number. For small capillary
numbers as $Ca<0.6$ for square microchannels there is a vortex in the reference frame moving with the bubble, which certainly influences and improves the corresponding mass transfer. 
Note that the flow
patterns strongly depend on the number of parameters as the slug length, the thickness of the
thickness and the existence of the vortex in front of the bubble. There are some available
correlations in literature \cite{bercic-mass,kreutzer-overview} and one of the particular goal of
this study is to study mass transfer dependence on the number of parameters. As well to validate or
to come up with another correlation describing the mass transfer.

@@

The volumetric mass transfer coefficient is calculated according to the work of
\citet{vanbaten-circular}. The concentration flux is calculated as the difference between overall
average concentration taken in the whole domain ($C_{overall}=\int_{V} C \mathrm{d}V /V$) 
{\color{red} (In this particular moment I don't know whether to take the Volume of whole domain or
just the liquid phase. I will go for whole domain.)}
at time
$t_1$ and time $t_2$ divided on the time difference $t_2-t_1$. Then the volumetric mass transfer
coefficient is calculated as:
\begin{equation}
\label{main:simulation:equation}
k_L a=\frac{\text{Flux}}{C_s-C_{outlet}} \frac{\text{bubble surface area}}{\text{unit cell volume}},
\end{equation}
where $C_{outlet}=\int{C U_{outlet}\mathrm{d}A}/\int{U_{outlet}\mathrm{d}A}$. 
{\color{red} Do not understand why we need this ratio bubble surface area/unit cell volume. In this
case the dimensional units do not coincide. In the calculations I will avoid it until further
clearance.}
To properly do
non-dimensioanalization one needs to insure the time conversion factor when the flux is calculated
inside the lattice Botlzmann system. The time conversion can be easily obtained:
\begin{equation}
\begin{aligned}
&U_{LB}=U_{phys}\frac{\Delta t}{\Delta x}\\
&\Delta t=\frac{U_{LB}}{U_{phys}}\Delta x\\
&\Delta t=\frac{1.5\,\mathrm{mm}}{200} \frac{0.0559}{0.902\,\mathrm{m/s}}=4.64\times
10^{-7}\,\mathrm{s} 
\end{aligned}
\end{equation}
We as well need to address the concentration being in a whole system non-dimensionalized towards the equilibrium:
if the domain size is

@@

The corresponding volumetric mass transfer coefficients depending on the velocity are indicated in
Table \ref{table:volumetric:coefficients}.

\section{Simulation results}
\subsection{Steady-state}
Using Eq.\ref{main:simulation:equation} we calculated the mass transfer coefficient. One can see
the plots for the mass transfer coefficient versus time in Fig. \ref{fig:steady:state}. We state as
a steady-state condition the average of concentration values between $500000$ to $1000000$ time steps. The values are presented 
\begin{figure}
\includegraphics[width=\textwidth]{Figures/steady_state.eps}
\caption{The mass transfer coefficient vs. time iterations. One can see that the pseudo steady
state can be reached after $500000$. The mass transfer coefficient is taken as the average of concentration values between $500000$ to $1000000$ time steps..\label{fig:steady:state}}
\end{figure}
